Convolutional Neural Networks on Graphs\\ with Fast Localized Spectral Filtering

### 2016-10-29 nips2016/nips2016.tex
tweaking for nips camera-ready, second submission (2016-10-28)

% Use less space
\usepackage{titlesec}		% space before / after headings
\titlespacing\section{0pt}{6pt plus 1pt minus 2pt}{1pt plus 1pt minus 2pt}
\titlespacing\subsection{0pt}{6pt plus 1pt minus 2pt}{1pt plus 1pt minus 2pt}
%\titlespacing\subsubsection{0pt}{10pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\setlength{\bibsep}{1.5pt} %comment for arxiv

\usepackage{parskip} \setlength{\parskip}{0pt} \setlength{\parindent}{1em}

\setlength{\textfloatsep}{7.2pt plus 1.0pt minus 2.0pt}
\setlength{\floatsep}{7.2pt plus 1.0pt minus 2.0pt}
\setlength{\intextsep}{7.2pt plus 1.0pt minus 2.0pt}

@@

\author{
  Michaël Defferrard \\ %\thanks{further info} \\
  %Department of Electrical Engineering \\
  %École Polytechnique Fédérale de Lausanne (EPFL) \\
  EPFL, Lausanne, Switzerland \\
  \texttt{michael.defferrard@epfl.ch} \\
  \And % \AND
  Xavier Bresson \\
  %School of Computer Science and Engineering \\
  Nanyang Technological University, Singapore \\
  \texttt{xavier.bresson@ntu.edu.sg} \\
  \And % \AND
  Pierre Vandergheynst \\
  %Department of Electrical Engineering \\
  EPFL, Lausanne, Switzerland \\
  \texttt{pierre.vandergheynst@epfl.ch} \\
}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\textwidth]{images/illustrationCNNgraphs}
\caption{Architecture of the proposed CNN on graphs.
	%Notation: $l$ is the coarsening level, $x^l$ are the downsampled signals at
	%layer $l$, $\G^l$ is the coarser graph, $g_{\theta^{K_l}}$ are the spectral
	%filters at layer $l$, $x_g^l$ are the filtered signals, $p_l$ is the
	%coarsening exponent, $n_c$ is the number of classes, $y$ is the output
	%signal, and $\theta^l$ is the number of parameters to learn at $l$.
}
\label{fig_illustration}
\end{figure}

@@

@@

Recall that the Chebyshev polynomial $T_k(x)$ of order $k$ may be generated by
the stable recurrence relation $T_k(x) = 2x T_{k-1}(x) - T_{k-2}(x)$ with $T_0 =
1$ and $T_1 = x$. These polynomials form an orthogonal basis for $L^2([-1,1], dy
/ \sqrt{1-y^2})$, the Hilbert space of square integrable functions with respect
to the measure $dy/\sqrt{1-y^2}$. A filter can thus be parametrized as a
truncated expansion of order $K-1$ such that
\begin{equation} \label{eq:filt_cheby}
	g_\theta(\Lambda) = \sum_{k=0}^{K-1} \theta_k T_k(\tilde{\Lambda}),
\end{equation}
where the parameter $\theta \in \R^K$ is a vector of Chebyshev coefficients and
$T_k(\tilde{\Lambda}) \in \R^{n \times n}$ is the Chebyshev polynomial of order
$k$ evaluated at $\tilde{\Lambda} = 2 \Lambda / \lambda_{max} - I_n$, a diagonal
matrix of scaled eigenvalues that lie in $[-1,1]$.

The filtering operation can then be written as $y = g_\theta(L) x
= \sum_{k=0}^{K-1} \theta_k T_k(\tilde{L}) x$, where $T_k(\tilde{L}) \in \R^{n
\times n}$ is the Chebyshev polynomial of order $k$ evaluated at the scaled
Laplacian $\tilde{L} = 2 L / \lambda_{max} - I_n$. %Note that the spectrum of the
%normalized Laplacian is bounded by $2$ \cite{book:Chung97Spectral}, such that
%the scaling can simply be $\tilde{L} = L - I_n$. 
Denoting $\bar{x}_k =
T_k(\tilde{L})x \in \R^n$, we can use the recurrence relation to compute
$\bar{x}_k = 2\tilde{L} \bar{x}_{k-1} - \bar{x}_{k-2}$ with $\bar{x}_0 = x$ and
$\bar{x}_1 = \tilde{L}x$. The entire filtering operation
\begin{equation}
	y = g_\theta(L) x = [\bar{x}_0, \ldots, \bar{x}_{K-1}] \theta
\end{equation}
then costs $\bO(K|\E|)$ operations.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\textwidth]{images/training}
\caption{Plots of validation accuracy and training loss for the first 2000
iterations on MNIST.}
\label{fig:convergence}
\end{figure}

>>>>

% Use less space
\usepackage{titlesec}		% space before / after headings
\titlespacing\section{0pt}{5pt plus 1pt minus 2pt}{1.8pt plus 1pt minus 1pt}
\titlespacing\subsection{0pt}{5pt plus 1pt minus 2pt}{2.7pt plus 1pt minus 2pt}
%\titlespacing\subsubsection{0pt}{10pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\setlength{\bibsep}{1.52pt} %comment for arxiv

\usepackage{parskip} \setlength{\parskip}{2.1pt} \setlength{\parindent}{1em}

\setlength{\textfloatsep}{8pt plus 1.0pt minus 2.0pt}
%\setlength{\floatsep}{8.2pt plus 1.0pt minus 2.0pt}
%\setlength{\intextsep}{8.2pt plus 1.0pt minus 2.0pt}

@@

\newcommand{\affe}{\textsuperscript{\dag}}
\newcommand{\affs}{\textsuperscript{\ddag}}

\author{
	Michaël Defferrard\affe \hspace{1cm} Xavier Bresson\affs \hspace{1cm} Pierre Vandergheynst\affe %\thanks{further info} \\
	%Department of Electrical Engineering \\
	%École Polytechnique Fédérale de Lausanne (EPFL) \\
	\vspace{0.2cm} \\
	\affe EPFL, Lausanne, Switzerland \hspace{1cm} \affs Nanyang Technological University, Singapore \\
	\texttt{\{michael.defferrard,pierre.vandergheynst\}@epfl.ch \hfill xavier.bresson@ntu.edu.sg} \\
}

%\author{
%  Michaël Defferrard \\ %\thanks{further info} \\
%  %Department of Electrical Engineering \\
%  %École Polytechnique Fédérale de Lausanne (EPFL) \\
%  EPFL, Lausanne, Switzerland \\
%  \texttt{michael.defferrard@epfl.ch} \\
%  \And % \AND
%  Xavier Bresson \\
%  %School of Computer Science and Engineering \\
%  Nanyang Technological University, Singapore \\
%  \texttt{xavier.bresson@ntu.edu.sg} \\
%  \And % \AND
%  Pierre Vandergheynst \\
%  %Department of Electrical Engineering \\
%  EPFL, Lausanne, Switzerland \\
%  \texttt{pierre.vandergheynst@epfl.ch} \\
%}

@@

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.87\textwidth]{images/illustrationCNNgraphs}
\caption{Architecture of the proposed CNN on graphs.
	%Notation: $l$ is the coarsening level, $x^l$ are the downsampled signals at
	%layer $l$, $\G^l$ is the coarser graph, $g_{\theta^{K_l}}$ are the spectral
	%filters at layer $l$, $x_g^l$ are the filtered signals, $p_l$ is the
	%coarsening exponent, $n_c$ is the number of classes, $y$ is the output
	%signal, and $\theta^l$ is the number of parameters to learn at $l$.
}
\label{fig_illustration}
\end{figure}

@@

Recall that the Chebyshev polynomial $T_k(x)$ of order $k$ may be generated by
the stable recurrence relation $T_k(x) = 2x T_{k-1}(x) - T_{k-2}(x)$ with $T_0 =
1$ and $T_1 = x$. These polynomials form an orthogonal basis for $L^2([-1,1], dy
/ \sqrt{1-y^2})$, the Hilbert space of square integrable functions with respect
to the measure $dy/\sqrt{1-y^2}$. A filter can thus be parametrized as a
truncated expansion of order $K-1$ such that
\begin{equation} \label{eq:filt_cheby}
	g_\theta(\Lambda) = \sum_{k=0}^{K-1} \theta_k T_k(\tilde{\Lambda}),
\end{equation}
where the parameter $\theta \in \R^K$ is a vector of Chebyshev coefficients and
$T_k(\tilde{\Lambda}) \in \R^{n \times n}$ is the Chebyshev polynomial of order
$k$ evaluated at $\tilde{\Lambda} = 2 \Lambda / \lambda_{max} - I_n$, a diagonal
matrix of scaled eigenvalues that lie in $[-1,1]$.
The filtering operation can then be written as $y = g_\theta(L) x
= \sum_{k=0}^{K-1} \theta_k T_k(\tilde{L}) x$, where $T_k(\tilde{L}) \in \R^{n
\times n}$ is the Chebyshev polynomial of order $k$ evaluated at the scaled
Laplacian $\tilde{L} = 2 L / \lambda_{max} - I_n$. %Note that the spectrum of the
%normalized Laplacian is bounded by $2$ \cite{book:Chung97Spectral}, such that
%the scaling can simply be $\tilde{L} = L - I_n$. 
Denoting $\bar{x}_k =
T_k(\tilde{L})x \in \R^n$, we can use the recurrence relation to compute
$\bar{x}_k = 2\tilde{L} \bar{x}_{k-1} - \bar{x}_{k-2}$ with $\bar{x}_0 = x$ and
$\bar{x}_1 = \tilde{L}x$. The entire filtering operation
	$y = g_\theta(L) x = [\bar{x}_0, \ldots, \bar{x}_{K-1}] \theta$
then costs $\bO(K|\E|)$ operations.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{images/training}
\caption{Plots of validation accuracy and training loss for the first 2000
iterations on MNIST.}
\label{fig:convergence}
\end{figure}
